Coherent optical creation of a single molecule

### 2020-12-18 fig-lifetime.tex
Move figures since PRX doesn't like subdirectories

\begin{tikzpicture}[scale=1.5391]
  \node at (0, 0) {\includegraphics[width=7.6958cm]{exp_data_norm_m_t.pdf}};
  \node at (-2.4, 1.2) {\footnotesize (\textbf{a})};

@@

  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{exp_data_norm_a_t.pdf}};
  \node at (-2.4, 1.2 - 2.7) {\footnotesize (\textbf{b})};
  % strength = 2pi 29.3(17) mHz/mW^2.58
  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{atomic_loss_scaling_inset.pdf}};
\end{tikzpicture}

>>>>

\begin{tikzpicture}[scale=1.5391]
  \node at (0, 0) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_m_t.pdf}};
  \node at (-2.4, 1.2) {\footnotesize (\textbf{a})};

@@

  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_a_t.pdf}};
  \node at (-2.4, 1.2 - 2.7) {\footnotesize (\textbf{b})};
  % strength = 2pi 29.3(17) mHz/mW^2.58
  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{imgs/atomic_loss_scaling_inset.pdf}};
\end{tikzpicture}

### 2020-12-18 fig-theory.tex
Move figures since PRX doesn't like subdirectories

\documentclass[border={-3pt -6pt -4pt -4pt}]{standalone} % left bottom right top
\usepackage{tikz}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  arrows.meta
}
\pgfdeclareradialshading{glow}{\pgfpoint{0cm}{0cm}}{
  color(0mm)=(white);
  color(5mm)=(white);
  color(9mm)=(black);
  color(10mm)=(black)
}

@@

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\fi

@@

\begin{tikzpicture}[scale=1.5391]
  \node at (0, 0) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_m_t.pdf}};
  \node at (-2.4, 1.2) {\footnotesize (\textbf{a})};

  \begin{scope}[shift={(0, 0.1)}]
    \node at (0.77, 0.5) {$t_{\mathrm{hold}}$};
    \draw[->,>=stealth,line width=1] (0.4, 0.5) -- (0, 0.5);
    \draw[->,>=stealth,line width=1] (1.1, 0.5) -- (1.5, 0.5);
    \draw[orange!80!white,line width=1,fill=orange!50!white]
    (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
    (0, 0.8) -- (0, 0.2);
    \draw[orange!80!white,line width=1,fill=orange!50!white,shift={(1.8, 0)}]
    (-0.3, 0.2) -- (-0.3, 0.8) -- node[above,orange!90!black] {\small $\pi$-pulse}
    (0, 0.8) -- (0, 0.2);
    \draw[->,>=stealth,line width=1] (-0.5, 0.2) -- (2, 0.2);
  \end{scope}

  \node at (0, -2.7) {\includegraphics[width=7.6958cm]{imgs/exp_data_norm_a_t.pdf}};
  \node at (-2.4, 1.2 - 2.7) {\footnotesize (\textbf{b})};
  % strength = 2pi 29.3(17) mHz/mW^2.58
  \node at (0.8, -2.25) {\includegraphics[width=4.6175cm]{imgs/atomic_loss_scaling_inset.pdf}};
\end{tikzpicture}

>>>>

\documentclass[border={-3pt -5.5pt -5pt -4pt}]{standalone} % left bottom right top

\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  arrows.meta
}
\pgfdeclareradialshading{glow}{\pgfpoint{0cm}{0cm}}{
  color(0mm)=(white);
  color(5mm)=(white);
  color(9mm)=(black);
  color(10mm)=(black)
}

@@

\ifpdf
% Ensure reproducible output
\pdfinfoomitdate=1
\pdfsuppressptexinfo=-1
\pdftrailerid{}
\hypersetup{
  pdfcreator={},
  pdfproducer={}
}
\fi

@@

\begin{tikzpicture}
  \node at (-9.8, 0) {\includegraphics[width=4.5cm]{imgs/RamanTransferScheme_v6.eps}};
  \node at (-11.4, 2.2) {\footnotesize (\textbf{a})};
  \node at (-1.35, 1.25) {\includegraphics[width=11.0cm]{imgs/raman_theory_full_gamma.pdf}};
  \node at (-7.05, 2.35) {\footnotesize (\textbf{b})};
  \node at (-4.35, -1.35) {\includegraphics[width=5.7cm]{imgs/raman_v0_vhi.pdf}};
  \node at (-6.95, -0.35) {\footnotesize (\textbf{c})};
  \node at (1.4, -1.35) {\includegraphics[width=5.7cm]{imgs/wavefunction.pdf}};
  \node at (-1.2, -0.35) {\footnotesize (\textbf{d})};
\end{tikzpicture}

### 2020-12-18 raman_spectroscopy_raman_beampath.tex
Move figures since PRX doesn't like subdirectories

\newcommand\drawellipseshade[5][inner color=black,outer color=black]{
  % 1: shading option
  % 2: center (x, y)
  % 3: xsize
  % 4: ysize
  % 5: angle
  \begin{scope}
    \clip[rotate around={#5:#2}] #2 ellipse ({#3} and {#4});
    \begin{scope}[transform canvas={shift={#2}, rotate=#5}]
      \shade[shading=radial,path fading=lens fading, #1] (0, 0) ellipse ({#3} and {#4});
    \end{scope}
  \end{scope}
}
% \newcommand\drawlens[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \drawellipseshade[inner color=blue,outer color=blue!40!cyan]{#1}{#2}{{0.14 * #2}}{#3}
% }
% \newcommand\drawwaveplate[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \drawellipseshade[inner color=blue!50!black,outer color=blue!80!black]{#1}{#2}{{0.07 * #2}}{#3}
% }
% \newcommand\drawaom[4]{
%   % 1: center (x, y)
%   % 2: xsize
%   % 3: ysize
%   % 4: angle
%   \drawellipseshade[inner color=orange,outer color=orange]{#1}{#2}{#3}{#4}
%   \begin{scope}[rotate around={#4:#1}]
%     \fill[orange, even odd rule, opacity=0.8]
%     ($#1 + ({#2}, 0)$) arc (0:360:{#2} and {#3})
%     -- ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
%     -- ($#1 + ({#2}, -{#3})$) --cycle;
%     \draw ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
%     -- ($#1 + ({#2}, -{#3})$) --cycle;
%   \end{scope}
% }
% \newcommand\drawpbs[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \begin{scope}
%     \begin{scope}
%       \clip[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
%       \begin{scope}[transform canvas={shift={#1}, rotate=#3}]
%         \shade[bottom color=blue!60!cyan, top color=blue!50!cyan, path fading=pbs fading]
%         (-{#2}, -{#2}) rectangle ({#2}, {#2});
%         \draw[line width=1] (-{#2}, -{#2}) -- ({#2}, {#2});
%       \end{scope}
%     \end{scope}
%     % Make sure the frame is not clipped
%     \draw[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
%   \end{scope}
% }
\newcommand\drawlens[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{lens.png}}};
  \end{scope}
}
\newcommand\drawwaveplate[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{wp.png}}};
  \end{scope}
}
\newcommand\drawaom[4]{
  % 1: center (x, y)
  % 2: xsize
  % 3: ysize
  % 4: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#4}] at (0, 0)
    {\scalebox{#2}[#3]{\includegraphics[width=2cm,height=2cm]{AOM.png}}};
  \end{scope}
}
\newcommand\drawpbs[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0)
    {\scalebox{#2}{\includegraphics[width=1.4285714285714286cm]{PBS.png}}};
  \end{scope}
}
\newcommand\drawmirror[4][line width=3]{
  % 1: draw option
  % 2: center (x, y)
  % 3: size
  % 4: angle
  \draw[#1] ($#2 + ({#3 * cos(#4)}, {#3 * sin(#4)})$) --
  ($#2 - ({#3 * cos(#4)}, {#3 * sin(#4)})$);
}

>>>>

\newcommand\drawellipseshade[5][inner color=black,outer color=black]{
  % 1: shading option
  % 2: center (x, y)
  % 3: xsize
  % 4: ysize
  % 5: angle
  \begin{scope}
    \clip[rotate around={#5:#2}] #2 ellipse ({#3} and {#4});
    \begin{scope}[transform canvas={shift={#2}, rotate=#5}]
      \shade[shading=radial,path fading=lens fading, #1] (0, 0) ellipse ({#3} and {#4});
    \end{scope}
  \end{scope}
}
% \newcommand\drawlens[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \drawellipseshade[inner color=blue,outer color=blue!40!cyan]{#1}{#2}{{0.14 * #2}}{#3}
% }
% \newcommand\drawwaveplate[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \drawellipseshade[inner color=blue!50!black,outer color=blue!80!black]{#1}{#2}{{0.07 * #2}}{#3}
% }
% \newcommand\drawaom[4]{
%   % 1: center (x, y)
%   % 2: xsize
%   % 3: ysize
%   % 4: angle
%   \drawellipseshade[inner color=orange,outer color=orange]{#1}{#2}{#3}{#4}
%   \begin{scope}[rotate around={#4:#1}]
%     \fill[orange, even odd rule, opacity=0.8]
%     ($#1 + ({#2}, 0)$) arc (0:360:{#2} and {#3})
%     -- ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
%     -- ($#1 + ({#2}, -{#3})$) --cycle;
%     \draw ($#1 + ({#2}, {#3})$) -- ($#1 + (-{#2}, {#3})$) -- ($#1 + (-{#2}, -{#3})$)
%     -- ($#1 + ({#2}, -{#3})$) --cycle;
%   \end{scope}
% }
% \newcommand\drawpbs[3]{
%   % 1: center (x, y)
%   % 2: size
%   % 3: angle
%   \begin{scope}
%     \begin{scope}
%       \clip[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
%       \begin{scope}[transform canvas={shift={#1}, rotate=#3}]
%         \shade[bottom color=blue!60!cyan, top color=blue!50!cyan, path fading=pbs fading]
%         (-{#2}, -{#2}) rectangle ({#2}, {#2});
%         \draw[line width=1] (-{#2}, -{#2}) -- ({#2}, {#2});
%       \end{scope}
%     \end{scope}
%     % Make sure the frame is not clipped
%     \draw[rotate around={#3:#1}] ($#1 - ({#2}, {#2})$) rectangle ($#1 + ({#2}, {#2})$);
%   \end{scope}
% }
\newcommand\drawlens[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{imgs/lens.png}}};
  \end{scope}
}
\newcommand\drawwaveplate[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0) {\scalebox{#2}{\includegraphics[width=2cm]{imgs/wp.png}}};
  \end{scope}
}
\newcommand\drawaom[4]{
  % 1: center (x, y)
  % 2: xsize
  % 3: ysize
  % 4: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#4}] at (0, 0)
    {\scalebox{#2}[#3]{\includegraphics[width=2cm,height=2cm]{imgs/AOM.png}}};
  \end{scope}
}
\newcommand\drawpbs[3]{
  % 1: center (x, y)
  % 2: size
  % 3: angle
  \begin{scope}[shift={#1}]
    \node[rotate={#3}] at (0, 0)
    {\scalebox{#2}{\includegraphics[width=1.4285714285714286cm]{imgs/PBS.png}}};
  \end{scope}
}
\newcommand\drawmirror[4][line width=3]{
  % 1: draw option
  % 2: center (x, y)
  % 3: size
  % 4: angle
  \draw[#1] ($#2 + ({#3 * cos(#4)}, {#3 * sin(#4)})$) --
  ($#2 - ({#3 * cos(#4)}, {#3 * sin(#4)})$);
}
